---
title: "MCQ scoring and scaling"
output: html_document

params:
  modcode: NA
  scored: NA
  dist: NA
  bins: NA
  
  

---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(numform)
library(kableExtra)
library(tidyverse)

# convert raw data to raw totals per student
#dist<-params$scored %>% group_by(SRN) %>% summarise(score=sum(score))

bins<-params$bins
scored<-params$scored
dist<-params$dist


gtable<-tibble(Grade=c("F-","F","F+","D-", "D", "D+", "C-", "C", "C+", "B-", "B", "B+", "A-", "A", "A+"),
               Min=unlist(strsplit(bins, split = ","))
)

   
            
   




       



#### MARKDOWN ----

```
### Processing marks for `r params$modcode`.
There were `r nrow(scored)` answers received
 from `r length(unique(scored$SRN))` students 
 answering `r length(unique(scored$name))` items.
 
### Raw total correct
```{r plot_raw, echo=FALSE, message=FALSE, warning=FALSE}
dist %>% ggplot(aes(x=score))+geom_bar()
```

The mean N correct was `r f_num(mean(dist$score),2)`.

The Module Leader identified `r gtable$Min[4]` as the minimum total required to Pass (D-) and `r gtable$Min[15]` as the minimum total required for A+.

The other grades were allocated equal bin widths between these two values, with the remainder allocated manually.

`r  kable_styling(kable(t(gtable),  align=c("r","l"), caption="Minimum total correct required for each Grade"),full_width=F)` 

### Grade distribution

Following scaling, the mean grade was `r f_num(mean(dist$grade),2)` (SD=`r f_num(sd(dist$grade),2)`).

The proportion of Upper-second/First class grades was
`r f_percent(100*nrow(dist |> filter(grade>=62))/nrow(dist),1)`

```{r plot_grades, echo=FALSE, message=FALSE, warning=FALSE}
# create grade plot labelled with N and percent
pct_format <- scales::percent_format(accuracy = .1)
    
dist %>% ggplot(aes(x=as.factor(grade)))+
       geom_bar() +
       #xlim(0,100)+
      xlab("Grade")+
       geom_text(
       aes(angle=90,
          label = sprintf(
             '%d (%s)',
             after_stat(count),
             pct_format(after_stat(count) / sum(after_stat(count)))
          )
       ),
       stat = 'count',
       nudge_y = 1,
       colour = 'darkblue',
       size = 4
    )+
      theme_minimal()


```




Produced : `r format(Sys.time(), "%a %b %d %X %Y")`

