---
title: "Statistical Moderation report"
output: word_document

params:
  modcode: NA
  marks: NA
  summary: NA
  origanova: NA
  orig.markers: NA
  orig.pairwise: NA
  modTable: NA
  modSummary: NA
  moderatedMarks: NA
  mod.markers: NA
  mod.pairwise: NA
 

---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(numform)

library(tidyverse)


# Conversion for grades to letters, linear categories 1-15, and classes
CATEGORICAL=tibble(Grade=c(0, 15 , 25, 38, 42, 45, 48, 52, 55, 58, 62, 65, 68, 77, 88, 100),
                   Category=0:15, 
                   Letter=c("Z","N-", "N", "N+", "D-", "D", "D+", "C-", "C", "C+", "B-", "B", "B+", "A-", "A", "A+"),
                   Class=c("Zero","Fail", "Fail", "Fail", "3rd", "3rd", "3rd", "2:II", "2:II", "2:II", "2:I", "2:I", "2:I", "1st", "1st", "1st"),
                   MClass= c("Zero","Fail", "Fail", "Fail", "Fail", "Fail", "Fail", "Pass", "Pass", "Pass", "Merit", "Merit", "Merit", "Dist", "Dist", "Dist")) 

CATEGORICAL$MClass<-ordered(CATEGORICAL$MClass, levels=c("Dist","Merit","Pass","Fail"))


distribution <- function(marks){
   marks %>% 
      ggplot(aes(x=Grade, fill=Class)) +
      geom_bar() +
      xlim(15,100) +
      scale_x_continuous(breaks=CATEGORICAL$Grade) +
      theme_classic()+guides(fill="none")
}

markersdensity <- function(marks){
   marks %>% ggplot(aes(x=Grade, group=Marker, colour=Marker))+
      geom_density() +
      xlim(0,100) +
      theme_classic()
}




origclasses <- params$marks %>% 
   group_by(Class) %>% 
      summarise(Orig=n()) %>% 
      mutate(OrigP=f_percent(100*Orig/sum(Orig)))


modClasses <- params$moderatedMarks %>% 
   group_by(Class) %>% 
       summarise(Mod=n()) %>% 
       mutate(ModP=f_percent(100*Mod/sum(Mod)))
 
modClasses<-left_join(origclasses, modClasses)

#### MARKDOWN ----

```
## Processing marks for `r params$modcode`.

`r params$summary`

## Pre  moderation distributions


```{r origDist, echo=FALSE, message=FALSE, warning=FALSE}
distribution(params$marks)

```

```{r origDensity, echo=FALSE, message=FALSE, warning=FALSE}

markersdensity(params$marks)
```

## Marker's details premoderation


`r knitr::kable(params$orig.markers, digits=2, caption="Markers' details from premoderated marks")`

`r params$origanova`

`r knitr::kable(params$orig.pairwise, digits=3, caption="Pairwise comparisons between Markers' premoderated marks")`


## Moderation

The following moderation values were applied:

`r knitr::kable(params$modTable, digits=1, caption="Grade adjustments for each marker")`

Grades were not moved above A+ (100%), or below the Fail boundary. No Failing grades were changed. For Undergraduate modules, the minimum passing grade is 42 (D-); for Masters modules, the minimum passing grade is C- (52).

`r params$modSummary`



```{r moddist, echo=FALSE, message=FALSE, warning=FALSE}

distribution(params$moderatedMarks)
```

```{r moddensity, echo=FALSE, message=FALSE, warning=FALSE}

markersdensity(params$moderatedMarks)
```



## Final marks

`r knitr::kable(params$mod.markers, digits=2, caption="Markers' details from moderated marks")`

`r knitr::kable(params$mod.pairwise, digits=3, caption="Pairwise comparisons between Markers' moderated marks")`

`r knitr::kable(modClasses,  caption="Proportions of classes in pre and post-moderation marks")`

