---
title: "Exam Collation report"
output: html_document

params:
  moderated: NA
  categorical: NA
  srn.errors: NA
  mark.errors: NA
  nomark.errors: NA
  checkable: NA
  minGrade: NA
  anonymise: NA

---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(numform)
library(tidyverse)
library(car)
library(psych)



# Report F(df1,df2)=xxx, p=.xxx
frep<-function(f.obj){
   s=paste0("F(", f.obj$Df[1],", ",f.obj$Df[2],")=",f_num(f.obj$`F value`[1],3),", ",f_pval(f.obj$`Pr(>F)`[1],alpha=.05,digits=3))
   return(s)
}

qanova<-function(df, q){
   
   if(length(unique(df$file))>1){
      r<-(tibble(Comparison=q, Analysis=frep(Anova(lm(data=df, moderated ~ file)))))
      } 
   if(length(unique(df$file))<2){
      r<-(tibble(Comparison=q, Analysis="Only one file; no comparisons made within Question"))
      }

   return(r)
}

# given a category, return a percent
percent<-function(x){
   categorical$percent[match(x,categorical$category)]
   
}

# given a percent, return a category
categorise<-function(x){
   if(params$minGrade=="4") 
   {class<-case_when(
      is.na(x) ~ "Zero",
      x==0 ~ "Zero",
      x<=39.99 ~ "Fail",
      x<=49.99 ~ "D: 3rd",
      x<=59.99 ~ "C: 2ii",
      x<=69.99 ~ "B: 2i",
      TRUE ~ "A: 1st"
      )}
   else
   {class<-case_when(
      is.na(x) ~ "Zero",
      x==0 ~ "Zero",
      x<=49.99 ~ "Fail",
      x<=59.99 ~ "C: Pass",
      x<=69.99 ~ "B: Merit",
      TRUE ~ "A: Dist"
      )}
}

qlist<-params$moderated %>% 
   group_by(question) %>% 
   group_modify(~ qanova(., .y$question))%>% 
   ungroup() %>% 
   select(-question) %>% 
   mutate(Comparison=str_remove(Comparison,".csv"))

exam.df<-params$checkable %>% 
         mutate(Grade=exammark) %>% 
         select(SRN, Grade) %>% 
         mutate(class=categorise(Grade)) 

sec.df<-params$checkable %>% 
   select(SRN, starts_with("Section"), exammark)



# exam.df is SRN, Grade, class

srn.errors<-params$srn.errors
mark.errors<-params$mark.errors
nomark.errors<-params$nomark.errors

if(params$anonymise=="Yes"){mark.errors<-mark.errors %>% select(-Email)}
if(params$anonymise=="Yes"){nomark.errors<-nomark.errors %>% select(-Email)}


tens<-c(0,10,20,30,40,50,60,70,80,90,100.01)

col_order<-c("question","A: Dist","B: Merit","C: Pass","A: 1st","B: 2i","C: 2ii","D: 3rd","Fail","Zero","Mean","SD")


exam.dist<-exam.df %>% 
   mutate(class=categorise(Grade)) %>% 
      ggplot(aes(x=Grade))+
   geom_histogram(aes(fill=class), breaks=tens-.01)+
   scale_x_continuous(breaks=tens)+
   xlab("Overall Exam Mark")+
   theme_classic()

exam.stats<-exam.df %>% 
   filter(!class=="Zero") %>%     # exclude Zeros from stats so % works
   group_by(class) %>% 
   summarise(students=n()) %>% 
   mutate(percentage=paste0(round(100*students/sum(students)),"%"))

exam.desc<-exam.df%>%   
  filter(!class=="Zero") %>%     # exclude Zeros from stats so % works
   summarise(Mean=round(mean(Grade, na.rm=T),2), 
             SD=round(sd(Grade, na.rm=T),2),
             Count=n())

# questions<-params$checkable %>% 
#    select(-starts_with("Section"), -exammark, -Email) %>% 
#    pivot_longer(-SRN) %>% 
#    filter(!is.na(value)) %>% 
#    mutate(name=str_remove(name,".csv"),
#           class=categorise(value))

questions<-params$moderated %>% 
   select(file, SRN, category, question, QName, percent )  %>% 
   mutate(class=categorise(percent))

# ques.dist<-params$checkable %>% 
#    select(-starts_with("Section"), -exammark, -Email) %>% 
#    pivot_longer(-SRN) %>% 
#    mutate(class=categorise(value)) %>% 
#    group_by(name, class) %>% 
#    summarise(count=n()) %>% 
#    filter(!class=="Zero") %>% 
#    ggplot(aes(x=name, y=count, fill=class))+
#    geom_col(position = "stack")+
#    theme_classic()

ques.dist<-questions  %>% 
   group_by(QName, class) %>% 
   summarise(count=n()) %>% 
   filter(!class=="Zero") %>% 
   ggplot(aes(x=as.factor(QName), y=count, fill=class))+
   xlab("Question")+
   geom_col(position = "stack")+
   theme_classic()

ques.mean<-questions %>%
   group_by(QName) %>% 
   summarise(Mean=round(mean(percent),1), SD=round(sd(percent),1) )

ques.stats<-questions %>% 
   group_by(QName, class) %>% 
   summarise(students=n()) %>% 
   mutate(students=paste(students,"(",round(100*students/sum(students)),"%)")) %>% 
   pivot_wider(names_from = class, values_from = students) %>% 
   select(intersect(col_order, names(.)))

ques.stats<-left_join(ques.stats,ques.mean)

ques.n<-questions %>% 
   group_by(SRN) %>% 
   summarise(n=n()) 
modal.n<-median(ques.n$n) 

sec.n<-ncol(sec.df)-2

sections<-sec.df %>% 
      pivot_longer(-SRN) %>% 
      mutate(class=categorise(value))
   
   sec.stats<-sections %>% 
      group_by(name, class) %>% 
      summarise(students=n()) %>% 
   mutate(students=paste(students,"(",round(100*students/sum(students)),"%)")) %>% 
   pivot_wider(names_from = class, values_from = students) %>% 
   select(intersect(col_order, names(.)))
   
   sec.mean<-sections %>% 
      group_by(name) %>% 
      
   summarise(Mean=round(mean(value, na.rm=T),1), 
             SD=round(sd(value, na.rm=T),1) )
   
   sec.stats<-left_join(sec.stats,sec.mean)
   


sec.dist<-sections  %>% 
   group_by(name, class) %>% 
   summarise(count=n()) %>% 
   filter(!class=="Zero") %>% 
   ggplot(aes(x=as.factor(name), y=count, fill=class))+
   xlab("Section")+
   geom_col(position = "stack")+
   theme_classic()# if(modal.n>1){
# qcorr.table<-corr.test(questions %>%
#    select(SRN,QName,percent) %>%
#    pivot_wider(names_from=QName, values_from=percent) %>% 
#    select(-SRN)
# )
# }

# scorr.table<-corr.test(sec.df)

#### MARKDOWN ----

```
`r if(nrow(srn.errors)>0) { knitr::kable(srn.errors,  caption="Scripts with incorrect SRNs (Please correct before continuing)")}` 
`r if(nrow(nomark.errors)>0) { knitr::kable(nomark.errors,  caption="Students with wrong number of marks (Please correct before continuing)")}`
`r if(nrow(mark.errors)>0) { knitr::kable(mark.errors,  caption="Marks not using Categorical Scale (Please correct before continuing) ")}`



`r if(length(qlist)>0) { knitr::kable(qlist,  caption="Differences between marksheets within questions (e.g., AA and in-person")}` 

## Questions

```{r plot_qfigs, echo=FALSE, message=FALSE, warning=FALSE}
            
if(exists("ques.stats")){knitr::kable(ques.stats,  caption="Question statistics") }
if(exists("ques.dist")){ques.dist}

# if(modal.n>1){
# 
#    pairs.panels(questions %>%
#    select(SRN,QName,percent) %>%
#    pivot_wider(names_from=QName, values_from=percent) %>% 
#    select(-SRN),lm=TRUE, stars=TRUE)
# }



```

## Sections and Examination

```{r plot_sfigs, echo=FALSE, message=FALSE, warning=FALSE}

if(exists("sec.stats")){knitr::kable(sec.stats,  caption="Section statistics") }
if(exists("sec.dist")){sec.dist}
if(sec.n>1){  
   try(pairs.panels(params$checkable %>% select(starts_with("Section"),exammark),lm=TRUE, stars=TRUE))
}


```

### Exam mean was `r exam.desc$Mean` with a standard deviation of `r exam.desc$SD` from `r exam.desc$Count` students.

```{r plot_efigs, echo=FALSE, message=FALSE, warning=FALSE}
if(exists("exam.dist")){exam.dist}


```



