---
title: "Dissertation Marking 2025"
# author: "Jon May"
# date: "30/04/2025"
output:
  pdf_document: default
  html_document: default
  word_document:
    reference_docx: word-reference.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
```{r functions, include=FALSE}
# define formatting functions
dp<-function(x,p){return(format(round(x, p), nsmall = p))}

# report p to three dp or <.001
pval<-function(p){
  s=paste0("p=",format(round(p,3), nsmall = 3))
  if(p<.001){s="p<.001"}
  return(s)}

# Report t(df1)=xxx, p=.xxx
trep<-function(t.obj){
  s=paste0("t(", dp(t.obj$parameter,1),")=",dp(t.obj$statistic,3),", ",pval(t.obj$p.value/2))
  return(s)
}
# Report F(df1,df2)=xxx, p=.xxx
frep<-function(f.obj){
  s=paste0("F(", f.obj$Df[1],", ",f.obj$Df[2],")=",dp(f.obj$`F value`[1],3),", ",pval(f.obj$`Pr(>F)`[1]))
  return(s)
}

#make functions to nicely report N and percent two ways
Npc<-function(num,tot){  # N (x%)
  paste0(num," (",round(100*num/tot, digits=0),"%)")
}

Npc2<-function(num,tot){ # (N, x%)
  paste0("(",num,", ",round(100*num/tot, digits=0),"%)")
}
```
```{r read and recode, include=FALSE}
library(tidyverse)
library(psych)
library(rio)


######## PARAMETERS TO CHANGE EACH YEAR ----

######## which modules to include
modulecodes<-c(605)

######## what year is it
ThisYear<-year(Sys.Date())

######## Data file paths
dlepath<-"marksheets"
datapath<-"surveydata"
s4path<-"enrolments"
allocationspath<-"allocations"



#### Find the name of the newest file in the folder named in datapath ----
files<-list.files(path=datapath, full.names = T)
fileinfo<-file.info(files) %>% arrange(desc(mtime))
datafile<-rownames(fileinfo)[1]
survey<-rio::import(datafile) # this assumes data has been exported as CSV with headers set to Question code
# ignore all entries before April this year
survey<-survey %>% #mutate(StartDate=dmy_hm(startdate)) %>% 
   filter(startdate>as.Date(paste0(ThisYear,"/04/01"))) %>% 
   filter(!is.na(SRN))

#### Read in any SRN corrections ----
srncorrections<-import("SRNcorrections.csv")
# This is a file with Wrong and Right SRNs
survey<-survey %>% 
   mutate(SRN=ifelse(SRN %in% srncorrections$Wrong, 
                        srncorrections$Right[match(SRN, srncorrections$Wrong)],
                        SRN))




#### read in gradebooks from dlepath ----

files<-list.files(path=dlepath, pattern=".csv", full.names = T)
dle<-rio::import_list(files, rbind=T) %>% 
   mutate(mod=str_sub(`_file`,13+str_length(dlepath),15+str_length(dlepath)))
status<-dle %>% 
   mutate(Status=str_sub(Status,1,6)) %>%  
   rename(Email=`Email address`) %>% 
   select(Email,Status,mod)

submitted<-status %>% filter(Status=="Submit")




#### read in enrolment lists from s4path ----

files<-list.files(path=s4path,  full.names = T)
s4<-rio::import_list(files, rbind=T)
s4<-s4 %>%
   rename(SRN=`Student Reference Number (SRN)`,
          Name=`Student: Account Name`,
          Email=`Student: Email`,
          Programme=`Stage: Programme: Programme Name`,
          Enrolment=`Enrolment Status`) %>%
   mutate(SRN=as.character(SRN),
          mod=str_sub(`_file`,-8,-6)) %>%
   select(SRN, Name, Email, Programme, Enrolment,mod) 

#### read in allocations from allocationspath ----

files<-list.files(path=allocationspath, full.names = T)
allocations<-rio::import_list(files, rbind=T) %>% 
   rename(Email=email) %>% mutate(SRN=as.character(SRN))

# Submissions

allocations<-left_join(s4,allocations)
students<-left_join(allocations,submitted)



# RECODINGS
grade.percent<-c(
"A+"=	100,
"A"	=88,
"A-"=	77,
"B+"=	68,
"B"	=65,
"B-"=	62,
"C+"=	58,
"C"	=55,
"C-"=	52,
"D+"=	48,
"D"	=45,
"D-"=	42,
"F+"=	38,
"F"=	25,
"F-"=	15,
"N"	=0,
"Inf"=NULL
)

percent.integer<-c(
"100"=	1,
"88"	=2,
"77"=	3,
"68"=	4,
"65"	=5,
"62"=	6,
"58"=	7,
"55"	=8,
"52"=	9,
"48"=	10,
"45"	=11,
"42"=	12,
"38"=	13,
"25"=	14,
"15"=	15,
"0"	=16
)

# convert letters to percents leaving missing values as -1
survey<-survey %>% 
  mutate(Super.pc = as.numeric(recode(SuperMark, !!!grade.percent)),
         Second.pc = as.numeric(recode(SecondMark, !!!grade.percent)),
         Agree.pc = as.numeric(recode(AgreedMark, !!!grade.percent)),
         SRN=as.character(SRN)# make a string
  ) %>% replace_na(list(Super.pc = -1, Second.pc = -1, Agree.pc=-1))


#### CORRECTIONS
# srn.recodes<-NULL
# # # these correct known mistakes in SRNs entered by staff
#
 # survey<-survey %>%
 #    mutate(SRN=recode(SRN, !!!srn.recodes))
# 
# # these spurious entries have been replaced by correct ones so can be deleted
# # 
survey<-survey %>% filter(!SRN=="12345678" & 
                          !SRN=="11111111" &
                          !SRN=="99999999")


# put all marks in one column
marks <- survey %>% 
  select(startdate, SRN, Super.pc,Second.pc,Agree.pc) %>%
  pivot_longer(Super.pc:Agree.pc, names_to = "Source", values_to = "Mark") %>% 
  filter(Mark>-1)

# put all comments in one column
comments <- survey %>% 
  select(startdate, SRN, SuperText, SecondText, AgreedText, AgreedNotes) %>%
    pivot_longer(SuperText:AgreedNotes, names_to = "Source", values_to = "text")


# concatenate any multiple comments per srn, reducing to one entry
comments <- comments %>% 
  filter(!is.na(text) & !text=="") %>% 
  select(-startdate) %>% 
  group_by(SRN,Source) %>% 
  summarise(text=toString(text)) %>% 
  mutate(text=ifelse(str_starts(text, ","),str_sub(text,3,-1),text)) %>%  # remove any ", " from start
  pivot_wider(names_from = "Source", values_from = "text")


# find the latest entry for each type of mark for each srn
dates<- marks %>% filter(Mark>0) %>% 
  group_by(SRN, Source) %>% 
  summarise(latest=max(startdate))

# find the actual last response
lastupdate<-max(dates$latest)

# only keep those where StartDate is the same as the latest entry and make one row per srn
srn <- left_join(marks, dates) %>%
  filter(startdate==latest) %>% 
  select(-latest, -startdate) %>% 
  pivot_wider(names_from = "Source", values_from = "Mark")

# prizes
prizes <- survey %>% 
   select(SRN, Prize) %>% 
   full_join(students %>% select(SRN, Name, Super)) %>% 
   filter(!is.na(Prize) & !Prize=="") %>% 
   select(SRN, Name, Super, Prize) %>% 
   arrange(SRN) %>% unique()




# copy marks into Student
marked<-students %>% full_join(srn)
# add in the comments
marked <- marked %>% full_join(comments)

# add in the sub status
#marked<-left_join(marked,status)

#get rid of empty columns
#marked<- marked %>% select (SRN:Project,Super.pc:Status)

# identify any spurious SRNs
spurious <- marked %>% 
  filter(is.na(Name)) %>% select(SRN,  Super.pc:Agree.pc)

spurious.n<-nrow(spurious)

# remove any that do not match required module list (from PARAMETERS)
marked<-marked %>% filter(mod %in% modulecodes)

#subset out those who have not submitted
nonsubmissions <-marked %>% filter(!Status=="Submit") #%>% select(SRN:Project)
marked<-marked %>% filter(Status=="Submit")


# save nonsubms
# write_csv(nonsubmissions,"nonsubmissions.csv")

# make a long list of marks for plotting
srn.long<- marked %>% pivot_longer(Super.pc:Agree.pc, names_to = "Source", values_to = "Mark") 

# count up projects done by each Supervisor
progress <- marked %>% 
   group_by(Super) %>% 
  summarise(First=n(), 
            agreed=sum(Agree.pc>0, na.rm=TRUE), 
            todo=First-agreed,
            mean=if_else(agreed>0,round(mean(Agree.pc, na.rm=TRUE),digits=2),0),
            sd=if_else(agreed>2,round(sd(Agree.pc, na.rm=TRUE),digits=2),0)
            )

complete <- progress %>% filter(todo==0)
incomplete <- progress %>% filter(todo>0)

agreed <- marked %>% filter(!is.na(Agree.pc)) %>% 
  select(SRN, Name, Super, Super.pc, Second, Second.pc, Agree.pc)

notagreed <- marked %>% filter(is.na(Agree.pc)) %>% 
  select(SRN, Name, Super, Super.pc, Second, Second.pc, Agree.pc)


# save parsed output for return to Supervisors and checking
marked %>%  select(SRN, Name, Email, Super, Second, Super.pc:AgreedNotes) %>% 
   full_join(prizes %>% select(SRN,Prize)) %>% 
  write_excel_csv(., paste0("DissertationMarks",toString(modulecodes),".csv"))

# save version of grading worksheet for upload if needed
 
fordle<-marked %>% select(Email, Agree.pc) %>% rename("Email address"="Email")
dlemodule<-dle %>% filter(mod==modulecodes)
fordle<-left_join(dlemodule,fordle) %>% 
  mutate(Grade=Agree.pc) %>% 
  select(-Agree.pc)
write_csv(fordle, "DLEGradesheetUploadable.csv")


## statistical section

# compute Supervisor agreememnt
inital.corr<-cor.test(agreed$Super.pc, agreed$Second.pc)
marks.r<-format(round(inital.corr$estimate, digits=3), nsmall=3)
marks.p<-paste0("=",format(round(inital.corr$p.value, digits=3), nsmall=3))
if(marks.p=="=0.000"){marks.p<-"<.001"}


distances<- marked %>% 
    mutate(Super.pc = as.numeric(recode(Super.pc, !!!percent.integer)),
         Second.pc = as.numeric(recode(Second.pc, !!!percent.integer)),
         Agree.pc = as.numeric(recode(Agree.pc, !!!percent.integer)),
         Difference =Super.pc-Second.pc
    ) %>% 
  group_by(Difference) %>% 
  summarise(Total=n()) %>% filter(!is.na(Difference))

mark.freqs<-marked %>% 
  group_by(Agree.pc) %>% 
  summarise(n=n())

check.agreed<-srn.long %>% filter(Mark>0) %>% filter(Source=="Agree.pc")
check.f<-anova(lm(data=check.agreed, Mark ~ Super))



```
## Results

By `r lastupdate`, `r  sum(agreed$Agree.pc>=0) ` marks have been agreed for the modules `r toString(modulecodes)`. 
There are `r nrow(submitted)` submissions summarised below. 

Total students remaining to be agreed is `r Npc(sum(progress$todo),sum(progress$First))`.

### Checking SRNs

`r nrow(srncorrections)` incorrect SRNs were corrected. 
`r if(nrow(srncorrections)>0) {knitr::kable(srncorrections, caption="Corrected SRNs")}`

`r spurious.n` unknown and uncorrected SRNS have been found in the entries provided.

`r if(spurious.n>0) {knitr::kable(spurious, caption="Unknown SRNs")}`



## `r nrow(complete)` Supervisors have completed mark entry.
`r knitr::kable(complete, caption="Marking Complete")`

Test of differences between Supervisors' Agreed marks: `r frep(check.f)`

## Nominations for the award of a prize.
`r knitr::kable(prizes, caption="Prize nominations", row.names=FALSE)`

## `r nrow(incomplete)` Supervisors have not completed mark entry.
`r knitr::kable(incomplete, caption="---")`


```{r plot_figs, echo=FALSE, message=FALSE, warning=FALSE}

# blobby plot of agreed marks for ewach supervisor
srn.long %>% filter(Mark>0) %>% filter(Source=="Agree.pc") %>% 
  ggplot(aes(y=Super, x=Mark, colour=Super))+
  #geom_jitter(width=.10, height=0)+
  geom_count()+
  guides(colour = "none")+
  xlim(40,100)+xlab("Supervisors' Agreed Marks")+
  theme_minimal()+
    # theme(axis.text.y = element_text(angle = 90, size=7, hjust=1))+
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank())


# density plot of grades from each source
srn.long %>% filter(Mark>0) %>% 
  ggplot(aes(x=Mark, group=Source, colour=Source))+
  scale_color_manual(values=c("red","blue","green"))+
  geom_density()+
  xlim(0,100)+
  theme_minimal()+
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank())

# column plot of grades from each source
srn.long %>% filter(Mark>0) %>% 
  ggplot(aes(x=as.factor(Mark), fill=Source))+
  scale_color_manual(values=c("red","blue","green"))+
  geom_bar(position="dodge")+
  xlab("Grade")+
  theme_minimal()+
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank())


mark.freqs %>% filter(Agree.pc>0) %>% 
  ggplot(aes(x=Agree.pc,y=n))+
  geom_col()+
  xlab("Agreed grade")+ylab("Count")+
  theme_minimal()+
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank())

srn %>% filter(Super.pc>0 & Second.pc>0) %>% 
  ggplot(aes(x=factor(Super.pc), y=factor(Second.pc)))+
  geom_jitter(height=.2, width=.2, size=.3)+
  xlab("Supervisor Grade")+ylab("Moderator Grade")+
  theme_minimal()


  



```

This frequency table shows the differences between initial grades (positive: Supervisor lower)
`r knitr::kable(distances, caption="Distances between Markers")`



Supervisors and Second Markers initial marks correlated `r marks.r`, p`r marks.p`.
\small
`r knitr::kable(agreed, caption="Marks agreed")`

`r knitr::kable(notagreed, caption="Not yet agreed")`


